---
output: html_document
title: "Main effects"
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, 
                      fig.path = "../output/main_effects/",
                      cache.path = "../cache/main_effects/",
                      cache.lazy = FALSE)
suppressMessages(silent <- lapply(
  c("knitr", "kableExtra", "tidyverse", "lme4", "lmerTest", "cowplot", "patchwork"), 
  library, character.only = TRUE))
```

```{r read-phenos}
phenos <- read_csv("../data/processed/ukb_phenos_unrelated.csv")
```

# Diet-biomarker relationships

We will focus on the relationship between the Mediterranean diet pattern, and specifically its sub-components of fish and omega-3 fatty acid intake, and two outcomes (hsCRP and TG, both log-transformed). These relationships have been established in prior observational and interventional research, so allow for the evaluation of the impact of various covariate adjustments, regression modeling strategies, and the impact of longitudinal data.

```{r hscrp-correlations}
expand_grid(
  v1 = c("hscrp_log", "tg_log", "ldl_statinadj", "bmi", "age"),
  v2 = c("hscrp_log", "tg_log", "ldl_statinadj", "bmi", "age")
) %>%
  rowwise() %>%
  mutate(corr = cor(phenos[[v1]], phenos[[v2]], use = "pairwise.complete.obs"),
         corr = round(corr, 2)) %>%
  ggplot(aes(x = v1, y = v2, fill = corr)) +
  geom_tile() +
  geom_text(aes(label = corr)) +
  scale_fill_continuous(name = "Pearson\ncorrelation") +
  theme(axis.title = element_blank())
```

```{r prep-diet-bm-regressions}
run_diet_bm_lm <- function(dv, bm, covars = c("age", "sex"), df = phenos,
                           std = FALSE) {
  if (std) df <- mutate(df, across(all_of(c(dv, bm)), ~ scale(.)))
  lm_str <- paste0(bm, " ~ ", dv, " + ", paste0(covars, collapse = " + "))
  lm_summ <- tryCatch({
    lm_fit <- lm(as.formula(lm_str), data = df) 
    lm_fit %>%
      broom::tidy() %>%
      filter(term == dv) %>%
      mutate(residual_df = lm_fit$df.residual)
  }, error = tibble(NA))
  lm_summ
}

mds_components <- c("VEG", "LEGUMES", "FRUIT", "NUTS", "FISH", "WHGRAIN", 
                   "MUFA2SFA", "REDPRMEAT", "ALC")
n3fa_variables <- c("FISH", "OILY_FISH", "oily_fish", "nonoily_fish", 
                    "N3FA", "N6FA",
                    paste0("fish_oil", c("_24hr", "_touchscreen", "_verbal")))
n3fa_variables_clean <- c(
  "Fish - 24HR", "Oily fish - 24HR",
  "Oily fish - FFQ", "Non-oily fish - FFQ",
  "Dietary N3FA - 24HR", "Dietary N6FA - 24HR",
  "Fish oil - 24HR", "Fish oil - touchscreen", "Fish oil - verbal interview"
)
key_bms <- c("hscrp_log", "tg_log", "ldl_statinadj")

minimal_covars <- c("age", "age_squared_std", "sex", "ageBySex_std")
ses_hl_covars <- c("ac", "income", "education", "smoking", "alcohol")
ffq_covars <- c("cooked_veg", "raw_veg", "fresh_fruit", "prmeat", "whole_bread")
covar_sets <- list(
  minimal = minimal_covars,
  adj = c(minimal_covars, ses_hl_covars),
  mdsAdj = c(minimal_covars, ses_hl_covars, "mds"),
  mdsCompAdj = c(minimal_covars, ses_hl_covars, 
                 setdiff(mds_components, c("FISH"))), #"MUFA2SFA", "ALC"))),
  ffqAdj = c(minimal_covars, ses_hl_covars, ffq_covars),
  ffqAdj_minusAC = setdiff(c(minimal_covars, ses_hl_covars, ffq_covars), "ac")
)
all_covars <- covar_sets$ffqAdj_minusAC

covar_set_labels <- c(
  minimal = "Minimal (age & sex)", adj = "+ SES & lifestyle",
  mdsAdj = "+ SES, lifestyle, & MDS", 
  mdsComp = "+ SES, lifestyle, & MDS components",
  ffqAdj = "+ SES, lifestyle, & FFQ diet traits",
  ffqAdj_minusAC = "Remove assessment center"
)

dv_bm_permutations <- expand_grid(
  dv = n3fa_variables,
  bm = key_bms
)

phenos <- phenos %>%
  mutate(age_squared_std = as.vector(scale(age_squared)),  # To avoid scale issues affecting LMM convergence
         ageBySex_std = as.vector(scale(ageBySex)),  # To avoid scale issues affecting LMM convergence
         income = ifelse(is.na(income), "Missing", income),  # Add missing indicators to SES & HL covariates rather than drop them
         education = ifelse(is.na(education), "Missing", education),
         across(all_of(c(ffq_covars, "bmi")), 
                ~ ifelse(is.na(.), median(., na.rm = TRUE), .)))
```

```{r n3fa-variables}
n3fa_var_corr_df <- expand_grid(
  var1 = n3fa_variables,
  var2 = n3fa_variables
) %>%
  rowwise() %>%
  mutate(corr_fit = list(broom::tidy(cor.test(phenos[[var1]], 
                                              phenos[[var2]])))) %>%
  unnest(corr_fit) %>%
  mutate(across(c(var1, var2), 
                ~ factor(., levels = n3fa_variables, 
                         labels = n3fa_variables_clean)))
n3fa_var_corr_df %>%
  ggplot(aes(x = var1, y = var2, fill = estimate)) +
  geom_tile() + 
  scale_fill_gradient2(name = "Pearson\ncorrelation") +
  labs(x = "", y = "", title = "Correlations between N3FA intake variables") +
  theme(axis.text.x = element_text(angle = 30, hjust = 0.9))
```

We start with some basic regression models for diet-biomarker main effects, using baseline visit data only, to explore variations on (1) different fish/omega-3 intake variables and (2) different degrees of covariate adjustment. Outcomes will be TG (positive control, with a well-established negative effect from RCTs) and hsCRP (the primary outcome of interest, which also has fairly substantial literature support). 

To retain the largest possible sample size, missing values in covariates (not primary exposures or outcomes) will be replaced by: 

* A "Missing" value (for categorical covariates)
* Median imputation (for numeric covariates)

```{r base-models, fig.asp = 1}
lm_res_df <- dv_bm_permutations %>%
  expand_grid(
    covar_set = names(covar_sets)
  ) %>% 
  rowwise() %>%
  mutate(model_res = list(run_diet_bm_lm(dv, bm, covars = covar_sets[[covar_set]],
                                         phenos, std = TRUE))) %>%
  unnest(model_res)

lm_res_df %>%
  mutate(l95 = estimate - 1.96 * std.error,
         u95 = estimate + 1.96 * std.error,
         covar_set = factor(covar_set, levels = names(covar_sets),
                            labels = covar_set_labels),
         dv = factor(dv, levels = n3fa_variables, 
                     labels = n3fa_variables_clean)) %>%
  ggplot(aes(x = dv, y = estimate, color = covar_set)) +
  geom_point(position=position_dodge(width=0.4)) +
  geom_errorbar(aes(ymin=l95, ymax=u95),
                position=position_dodge(width=0.4), width=0.2) +
  geom_hline(yintercept=0, color="gray") + 
  scale_color_discrete(name = "Adjustment set") + 
  labs(x = "Diet variable",
       y = "Standardized effect estimate (95% CI)",
       title = "Fish effect estimates from linear regression") +
  facet_wrap(~bm, nrow = 3, scales = "free_y") +
  theme(axis.text.x = element_text(angle = 30, hjust = 0.9))
```

```{r ac-model-comparison, eval = F}
lm_with_ac <- lm(
  as.formula(paste0("hscrp_log ~ oily_fish + ", 
                    paste(covar_sets$ffqAdj, collapse = " + "))),
  data = phenos
)
lm_without_ac <- lm(
  as.formula(paste0("hscrp_log ~ oily_fish + ", 
                    paste(covar_sets$ffqAdj_minusAC, collapse = " + "))),
  data = phenos
)

lmtest::lrtest(lm_without_ac, lm_with_ac)
```

We note a few things from these results.

* Covariate adjustment generally reduces estimated effect magnitudes by a substantial amount, likely due to fish intake being correlated with other health-associated behaviors and traits.
* Oily fish (from FFQ) has a much stronger association with both outcomes than fish variables from 24HR or non-oily fish.
* Fish oil effect estimates from different sources (24HR, touchscreen questionnaire, and verbal interview) are reasonably consistent, despite their very modest correlation with each other.
* Adjustment for dietary intake variables from FFQ (cooked and raw vegetables, fresh fruit, processed meat, and choice of wholegrain bread) is an alternative to adjustment for the MDS and its components as an approach to addressing confounding by more general healthfulness of diet. Here, this strategy achieves almost as much attenuation of effect estimates (especially for oily fish) while allowing for much larger sample sizes (~2x). Notably, the degree of effect size attenuation is "weakest" specifically for intake variables derived from 24HR.
* Removal of the assessment center adjustment, which adds to statistical and computational burden by requiring tens of binary indicator variables, doesn't appear to meaningfully change effect estimates.
* Standardized effect size estimates for oily fish, fish oil, and N3FA intake are remarkably consistent in fully adjusted models.

Based on the results above, we will move forward using oily fish intake (from FFQ) as the primary dietary exposure variable, with adjustment for SES (minus assessment center), healthy lifestyle, and other FFQ-measured dietary factors.

# Incorporate NMR metabolomics

We have access to quantified omega-3 and omega-6 fatty acid measurements in blood based on the Nightingale NMR platform. First, we look at raw correlations between fish intake variables, biomarkers, and relevant FA quantities.

```{r prep-nmr}
pufa_metabolites <- c("Omega_3", "Omega_6",
                    "Omega_3_pct", "Omega_6_pct",
                    "Omega_3_pct_PUFA", "Omega_6_pct_PUFA",
                    "Omega_6_by_Omega_3",
                    "DHA", "DHA_pct")

phenos <- mutate(phenos, nonDHA_pct = Omega_3_pct - DHA_pct)
```

```{r ffq-imputed-n3fa}
n3fa_impute_vars <- c("oily_fish", "nonoily_fish", "fish_oil_touchscreen", "fish_oil_verbal")
n3fa_impute_lm_fit <- lm(
  as.formula(paste0("Omega_3_pct ~ ", paste(n3fa_impute_vars, collapse = " + "))),
  data = phenos)
n3fa_impute_df <- phenos %>%
  select(all_of(n3fa_impute_vars)) %>%
  mutate(across(contains("fish_oil"), ~ if_else(is.na(.x), 0, .x)))
n3fa_impute_df$dn3fa <- predict(n3fa_impute_lm_fit, newdata = n3fa_impute_df)
phenos$dn3fa <- n3fa_impute_df$dn3fa

n3fa_impute_weights_df <- broom::tidy(n3fa_impute_lm_fit) %>%
  filter(term != "(Intercept)") %>%
  select(term, weight = estimate)
n3fa_impute_weights_df %>%
  kable(caption = "Weights for fish and fish oil-based N3FA intake estimation:") %>%
  kable_styling(full_width = FALSE)

more_lm_res_df <- expand_grid(
  dv = c("oily_fish", "fish_oil_touchscreen", "dn3fa"),
  bm = c("hscrp_log", "tg_log", "ldl_statinadj"),
  covar_set = "ffqAdj"
  ) %>% 
  rowwise() %>%
  mutate(model_res = list(run_diet_bm_lm(dv, bm, covars = covar_sets[[covar_set]],
                                         phenos, std = TRUE))) %>%
  unnest(model_res)

n3fa_variables <- c(n3fa_variables, "dn3fa")
n3fa_variables_clean <- c(n3fa_variables_clean, "Estimated dietary N3FA")

more_lm_res_df %>%
  mutate(l95 = estimate - 1.96 * std.error,
         u95 = estimate + 1.96 * std.error,
         covar_set = factor(covar_set, levels = names(covar_sets),
                            labels = covar_set_labels),
         dv = factor(dv, levels = n3fa_variables, 
                     labels = n3fa_variables_clean)) %>%
  ggplot(aes(x = dv, y = estimate, color = covar_set)) +
  geom_point(position=position_dodge(width=0.4)) +
  geom_errorbar(aes(ymin=l95, ymax=u95),
                position=position_dodge(width=0.4), width=0.2) +
  geom_hline(yintercept=0, color="gray") + 
  scale_color_discrete(name = "Adjustment set") + 
  labs(x = "Diet variable",
       y = "Standardized effect estimate (95% CI)",
       title = "Fish effect estimates from linear regression") +
  facet_wrap(~bm, nrow = 1, scales = "free_y") +
  theme(axis.text.x = element_text(angle = 30, hjust = 0.9))

lm_res_df <- bind_rows(
  filter(lm_res_df, dv != "dn3fa"),
  filter(more_lm_res_df, dv == "dn3fa")
)
```

```{r nmr-corrs}
pheno_corr_df <- expand_grid(
  var1 = c(n3fa_variables, key_bms, pufa_metabolites),
  var2 = c(n3fa_variables, key_bms, pufa_metabolites)
) %>%
  rowwise() %>%
  mutate(corr_fit = list(broom::tidy(cor.test(phenos[[var1]], 
                                              phenos[[var2]])))) %>%
  unnest(corr_fit)

pheno_corr_df %>%
  mutate(across(c(var1, var2), ~ fct_relevel(., c(n3fa_variables, key_bms, pufa_metabolites)))) %>%
  ggplot(aes(x = var1, y = var2, fill = estimate)) +
  geom_tile() + 
  scale_fill_gradient2() +
  labs(x = "", y = "") +
  theme(axis.text.x = element_text(angle = 30, hjust = 0.9))

pheno_corr_df %>%
  filter(var1 == "oily_fish",
         var2 %in% pufa_metabolites) %>%
  mutate(estimate = round(estimate, 2)) %>%
  arrange(desc(abs(estimate))) %>%
  select(`FA measurement` = var2, Correlation = estimate) %>%
  kable(caption = "Correlations of FA metabolites with oily fish intake") %>%
  kable_styling(full_width = FALSE)
```

We see that oily fish is the most strongly-correlated fish intake measurement not just with biomarkers, but also with blood N3 and N6 concentrations. Looking more closely at the oily fish-FA correlations, the strongest magnitudes involve N3 and DHA percentages of total fatty acids, though absolute concentrations are also similar (along with N6 quantities that directly trade off with N3, such as % of PUFA or N6:N3 ratio).

Do we have evidence that the N3 percentage mediates any proportion of the relationship between oily fish intake and inflammation? Unlike the above, this mediation analysis will incorporate the full set of confounder adjustments used above.

```{r nmr-mediation, cache = 1}
test_mediation_std <- function(x, m, y, covars, df) {
  df <- df %>%
    select(all_of(c(x, m, y, covars))) %>%
    na.omit() %>%
    mutate(across(all_of(c(x, m, y)), \(x) as.vector(scale(x))))
  med_form_str <- paste0(m, " ~ ", x, " + ", 
                         paste(covars, collapse = " + "))
  med_fit <- lm(as.formula(med_form_str), data = df)
  out_form_str <- paste0(y, " ~ ", m, " + ", x, " + ",
                         paste(covars, collapse = " + "))
  out_fit <- lm(as.formula(out_form_str), data = df)
  med_out <- mediation::mediate(med_fit, out_fit, treat = x, mediator = m, 
                                robustSE = TRUE, sims = 20)
  med_out$model.m <- NULL
  med_out$model.y <- NULL
  med_out
}

med_design_df <- expand_grid(
  e = c("oily_fish", "fish_oil_touchscreen", "dn3fa"),
  m = c("Omega_3_pct", "DHA_pct", "nonDHA_pct"),
  y = c("hscrp_log")
)
std_med_res_df <- med_design_df %>%
  rowwise() %>%
  mutate(med_obj = list(test_mediation_std(e, m, y, all_covars, phenos)),
         tau.coef = map_dbl(list(med_obj), \(x) x$tau.coef),
         tau.p = map_dbl(list(med_obj), \(x) x$tau.p),
         d.avg = map_dbl(list(med_obj), \(x) x$d.avg),
         d.avg.p = map_dbl(list(med_obj), \(x) x$d.avg.p),
         z.avg = map_dbl(list(med_obj), \(x) x$z.avg),
         z.avg.p = map_dbl(list(med_obj), \(x) x$z.avg.p),
         n.avg = map_dbl(list(med_obj), \(x) x$n.avg),
         n.avg.p = map_dbl(list(med_obj), \(x) x$n.avg.p))
```

```{r nmr-mediation-viz}
std_med_res_df %>%
  select(-med_obj, -contains(".p")) %>%
  pivot_longer(c(contains(".avg"), tau.coef), names_to = "quantity", values_to = "value") %>%
  filter(
    # y == "hscrp_log",
    quantity != "n.avg",
    quantity != "z.avg") %>%
  mutate(quantity = factor(quantity,
                           levels = c("tau.coef", "d.avg"),
                           labels = c("Total effect", "Mediated effect"))) %>%
  ggplot(aes(x = m, y = value, fill = quantity)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  scale_fill_discrete(name = "") +
  facet_grid(rows = vars(y), cols = vars(e), scales = "free_y") +
  labs(x = "Plasma N3FA fraction", y = "Std. effect (SDy/SDx)") +
  theme(axis.text.x = element_text(angle = 25, hjust = 0.9))
```

```{r nmr-mediation-neg-controls, cache = 1}
nc_med_design_df <- expand_grid(
  e = c("dn3fa", "oily_fish", "nonoily_fish", "raw_veg"),
  m = c("Omega_3_pct"),
  y = c("hscrp_log")
)
std_nc_med_res_df <- nc_med_design_df %>%
  rowwise() %>%
  mutate(med_obj = list(test_mediation_std(e, m, y, all_covars, phenos)),
         tau.coef = map_dbl(list(med_obj), \(x) x$tau.coef),
         tau.p = map_dbl(list(med_obj), \(x) x$tau.p),
         d.avg = map_dbl(list(med_obj), \(x) x$d.avg),
         d.avg.p = map_dbl(list(med_obj), \(x) x$d.avg.p),
         z.avg = map_dbl(list(med_obj), \(x) x$z.avg),
         z.avg.p = map_dbl(list(med_obj), \(x) x$z.avg.p),
         n.avg = map_dbl(list(med_obj), \(x) x$n.avg),
         n.avg.p = map_dbl(list(med_obj), \(x) x$n.avg.p))
```

These mediation results suggest that approximately all of the oily fish-hsCRP relationship is mediated through the effect of oily fish on blood N3 levels. This is not surprising mechanistically, and even suggests that blood N3 concentrations (or percentage) might be a more effective measure of the biologically relevant components of the fish intake exposure than self-reported components. Notably, a second mediation analysis that contains only minimal covariate adjustment (age & sex) retains a modestly significant ADE and a proportion mediated that is less than one. This is a nice negative control of sorts, because we expect blood N3 levels to mediate the effect of fish intake, but not the effect of other lifestyle and socioeconomic factors correlated with fish intake.

# Export datasets for interaction modeling and manuscript

```{r export-modeling}
gwis_bms <- c("hscrp_log", "tg_log", "ldl_statinadj")
gwis_variables <- c("id", 
                    gwis_bms, 
                    c(n3fa_variables, "fish_oil"), 
                    pufa_metabolites, 
                    all_covars, paste0("gPC", 1:10))

gwis_df <- phenos %>%
  filter(if_all(all_of(c(gwis_bms, all_covars)), ~ !is.na(.))) %>%
  mutate(fish_oil = fish_oil_touchscreen)

mm_form <- as.formula(paste("~ 1 + ", paste(gwis_variables, collapse = " + ")))
gwis_mat <- model.matrix(
  mm_form, 
  model.frame(mm_form, gwis_df, na.action = na.pass)
)[, -1]  # Need intercept in formula to drop level from each factor, but don't want to keep it
colnames(gwis_mat) <- make.names(colnames(gwis_mat))
gwis_covars <- setdiff(colnames(gwis_mat), 
                       c("id", gwis_bms, n3fa_variables, "fish_oil", pufa_metabolites))
write(gwis_covars, "../data/processed/gwis_covariates.txt")
write_csv(as_tibble(gwis_mat), "../data/processed/ukb_gwis_phenos.csv")
```

```{r export-manuscript}
saveRDS(covar_sets, "../data/processed/manuscript/covar_sets_list.rds")
saveRDS(covar_set_labels, "../data/processed/manuscript/covar_set_labels.rds")
saveRDS(phenos, "../data/processed/manuscript/phenos.rds")
saveRDS(lm_res_df, "../data/processed/manuscript/lm_res_df.rds")
saveRDS(pheno_corr_df, "../data/processed/manuscript/pheno_corr_df.rds")
saveRDS(n3fa_impute_weights_df, "../data/processed/manuscript/n3fa_impute_weights_df.rds")
saveRDS(std_med_res_df, "../data/processed/manuscript/std_med_res_df.rds")
saveRDS(std_nc_med_res_df, "../data/processed/manuscript/std_nc_med_res_df.rds")
```

# Archive

```{r nmr-mediation-old, cache = 1, eval = F}
test_mediation <- function(x, m, y, covars, df) {
  df <- df %>%
    select(all_of(c(x, m, y, covars))) %>%
    na.omit()
  med_form_str <- paste0(m, " ~ ", x, " + ", 
                         paste(covars, collapse = " + "))
  med_fit <- lm(as.formula(med_form_str), data = df)
  out_form_str <- paste0(y, " ~ ", m, " + ", x, " + ",
                         paste(covars, collapse = " + "))
  out_fit <- lm(as.formula(out_form_str), data = df)
  med_out <- mediation::mediate(med_fit, out_fit, treat = x, mediator = m, 
                                robustSE = TRUE, sims = 100)
  med_out
}

main_med_obj <- test_mediation(
  "oily_fish", "Omega_3_pct", "hscrp_log", all_covars, phenos
)

unadj_med_obj <- test_mediation(
  "oily_fish", "Omega_3_pct", "hscrp_log", covar_sets$minimal, phenos
)

no_med_obj <- test_mediation(
  "nonoily_fish", "Omega_3_pct", "hscrp_log", all_covars, phenos
)

neg_control_obj <- test_mediation(
  "raw_veg", "Omega_3_pct", "hscrp_log", all_covars, phenos
)

print("Primary oily fish mediation test:")
plot(main_med_obj, main = "Primary oily fish mediation test", xlim = c(-0.5, 0))
summary(main_med_obj)
print("Minimally-adjusted mediation test:")
plot(unadj_med_obj, main = "Minimally-adjusted mediation test", xlim = c(-0.5, 0))
summary(unadj_med_obj)
print("Non-oily fish mediation test:")
plot(no_med_obj, main = "Non-oily fish mediation test", xlim = c(-0.5, 0))
summary(no_med_obj)
print("Raw vegetable intake mediation test (healthy lifestyle negative control):")
plot(neg_control_obj, main = "Raw vegetable intake mediation test (healthy lifestyle negative control)", 
     xlim = c(-0.02, 0))
summary(neg_control_obj)

print("FFQ_N3FA - N3FA - hsCRP:")
dn3fa_med_obj <- test_mediation(
  "dn3fa", "Omega_3_pct", "hscrp_log", all_covars, phenos
)
summary(dn3fa_med_obj)

print("Fish oil - N3FA - hsCRP:")
fish_oil_med_obj <- test_mediation(
  "fish_oil_touchscreen", "Omega_3_pct", "hscrp_log", all_covars, phenos
)
summary(fish_oil_med_obj)

print("Oily fish - N3FA - TG:")
tg_med_obj <- test_mediation(
  "oily_fish", "Omega_3_pct", "tg_log", all_covars, phenos
)
summary(tg_med_obj)

print("Oily fish - N3FA - LDL:")
ldl_med_obj <- test_mediation(
  "oily_fish", "Omega_3_pct", "ldl_statinadj", all_covars, phenos
)
summary(ldl_med_obj)

print("Oily fish - N3FA - LDL, w/ BMI adj:")
ldl_med_bmiAdj_obj <- test_mediation(
  "oily_fish", "Omega_3_pct", "ldl_statinadj", c(all_covars, "bmi"), phenos
)
summary(ldl_med_bmiAdj_obj)

print("Oily fish - DHA - hsCRP:")
dha_med_obj <- test_mediation(
  "oily_fish", "DHA_pct", "hscrp_log", all_covars, phenos
)
summary(dha_med_obj)

print("Oily fish - EPA - hsCRP:")
epa_med_obj <- test_mediation(
  "oily_fish", "nonDHA_pct", "hscrp_log", all_covars, phenos
)
summary(epa_med_obj)
```
