---
output: html_document
title: "Phenotype QC"
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = FALSE, message = FALSE,warning = FALSE, 
                      fig.path = "../output/phenos_summary/")
suppressMessages(silent <- lapply(
  c("knitr", "kableExtra", "tidyverse", "cowplot", "patchwork"), 
  library, character.only = TRUE))
```

```{r read-phenos}
raw_phenos <- read_csv("../data/processed/ukb_phenos_longitudinal_raw.csv")
phenos <- read_csv("../data/processed/ukb_phenos_longitudinal_unrelated.csv")
```

## Exclusion criteria

* No diabetes (self-report of diagnosed diabetes; field 2443)
* No coronary heart disease (self-report of diagnosed MI or angina; field 6150)
* No liver cirrhosis (ICD-10 codes K70.2-4, K71.7, K74.X; field 41202 (primary) or 41204 (secondary))
* No cancer diagnosis within a year prior to assessment center visit
* Not pregnant

```{r exclusion-criteria}
raw_phenos %>%
  select(id, diabetes, CHD, cirrhosis, cancer_within_1yearac, pregnant) %>%
  pivot_longer(-id, names_to="criterion") %>%
  group_by(criterion) %>%
  summarise(Yes = sum(value),
            No = sum(!value)) %>%
  mutate(criterion = c(
    cancer_within_1yearac="Cancer status (within one year prior to baseline)",
    CHD="CHD", cirrhosis = "Cirrhosis", diabetes = "Diabetes", 
    pregnant = "Pregnant"
  )[criterion]) %>%
  setNames(c("Exclusion criterion", "Yes", "No")) %>%
  kable(caption = "Sample counts for exclusion criteria") %>%
  kable_styling(full_width = FALSE)

raw_phenos %>%
  filter(!diabetes, !CHD, !cirrhosis, !cancer_within_1yearac, !pregnant) %>%
  group_by(instance) %>%
  summarise(N = n()) %>%
  setNames(c("Instance", "N")) %>%
  kable(caption = "Sample sizes after exclusions") %>%
  kable_styling(full_width = FALSE)
```

# Sample sizes

```{r sample-sizes}
selected_phenos <- phenos %>%
  filter(instance == 0) %>%
  select(id, hscrp_log, oily_fish, Omega_3_pct, ALC, VEG, mds)
pheno_nonmissingness_list <- lapply(select(selected_phenos, -id), 
                                    function(x) phenos$id[which(!is.na(x))])

UpSetR::upset(UpSetR::fromList(pheno_nonmissingness_list),
                               nsets = length(pheno_nonmissingness_list),
                               nintersects = NA)
```

## Biomarker preprocessing

```{r biomarkers}
cm_biomarker_fields <- c(
  alt = 30620, alb = 30600, apoB = 30640, hscrp = 30710, chol = 30690, glu = 30740, 
  hba1c = 30750, hdl = 30760, ldl = 30780, shbg = 30830, tg = 30870, vitD = 30890,
  sbp = 4080, dbp = 4079
)

biomarkers_raw <- names(cm_biomarker_fields)

statinadj_biomarkers <- c("apoB", "chol", "ldl")
medsadj_biomarkers <- c("sbp", "dbp")
logged_biomarkers <- c("alt", "hscrp", "tg")

biomarkers <- biomarkers_raw
biomarkers <- ifelse(biomarkers %in% statinadj_biomarkers,
                     paste0(biomarkers_raw, "_statinadj"),
                     biomarkers)
biomarkers <- ifelse(biomarkers %in% medsadj_biomarkers,
                     paste0(biomarkers_raw, "_medsadj"),
                     biomarkers)
biomarkers <- ifelse(biomarkers %in% logged_biomarkers,
                     paste0(biomarkers_raw, "_log"),
                     biomarkers)

biomarkers_clean <- c(
  "Alanine aminotransferase", "Albumin", "Apolipoprotein B", "High-sensitivity C-reactive protein", 
  "Total cholesterol", "Random glucose", "Glycated hemoglobin", 
  "High-density lipoprotein cholesterol", "Low-density lipoprotein cholesterol",
  "Sex hormone-binding globulin", "Triglycerides", "Vitamin D",
  "Systolic blood pressure", "Diastolic blood pressure"
)
biomarkers_short <- c(
  "ALT", "Alb", "ApoB", "hsCRP", "TC", "RG", "HbA1c", "HDL-C", "LDL-C", "SHBG", 
  "TG", "VitD", "SBP", "DBP"
)

biomarker_groups <- c(
  "Liver", "Liver", "Lipids", "Inflammation", "Lipids", "Glycemic", "Glycemic",
  "Lipids", "Lipids", "Other", "Lipids", "Other", "Blood pressure", "Blood pressure"
)

# biomarker_units <- c(
#   "U/L", "g/L", "U/L", "g/L", "g/L", "U/L", "mg/L", "mmol/L", "mmol/L", "umol/L",
#   "mg/L", "umol/L", "U/L", "mmol/L", "mmol/mol", "mmol/L", "nmol/L", "mmol/L",
#   "nmol/L", "pmol/L", "mmol/L", "IU/mL", "nmol/L", "nmol/L", "umol/L", "g/L",
#   "mmol/L", "umol/L", "mmol/L", "nmol/L"
# )

analytical_ranges <- list(
  alt = c(3, 500), alb = c(15, 60), alp = c(5, 1500), apoA = c(0.4, 2.5), apoB = c(0.4, 2), 
  ast = c(3, 1000), hscrp = c(0.08, 80), Ca = c(1, 5), chol = c(0.5, 18), creatinine = c(0, 4420), 
  cysC = c(0.1, 8), bilirubin_dir = c(0, 171), ggt = c(5, 1200), glu = c(0.6, 45), hba1c = c(15, 184), 
  hdl = c(0.05, 4.65), igf1 = c(1.3, 195), ldl = c(0.26, 10.3), lipA = c(5.76, 189), oestradiol = c(73, 17621), 
  phos = c(0.32, 6.4), rheum_factor = c(10, 120), shbg = c(0.33, 233), tes = c(0.35, 55.52), 
  bilirubin_tot = c(0, 513), protein_tot = c(30, 120), tg = c(0.1, 11.3), urate = c(89, 1785), 
  urea = c(0.8, 50), vitD = c(10, 375) 
)

tibble(
  Biomarker = biomarkers_clean,
  Abbreviation = biomarkers_short,
  Group = biomarker_groups,
  `UKB Field` = cm_biomarker_fields,
) %>%
  mutate(`Log-transformed` = ifelse(biomarkers_raw[match(Biomarker, biomarkers_clean)]
                                    %in% logged_biomarkers, "Yes", "No")) %>%
  kable(caption = "Cardiometabolic biomarkers measured in the UK Biobank") %>%
  kable_styling(full_width = FALSE)
```

The following QC and preprocessing steps were performed on raw blood biomarker data from the main assessment center visit:

1. Adjust for statin usage where appropriate (TC, LDL-C, and ApoB)
2. Log-transform for substantially non-normal biomarkers (ALT, TG, hsCRP, CBC-based inflammatory indices)
3. Winsorize biomarker distributions at 5 SDs from the mean.

Note: These preprocessing steps were undertaken in the full dataset (prior to removing related individuals).

### Biomarker distributions

These distributions contain all available values, including repeat measurements per individual where available.

Dashed lines in raw biomarker histograms denote the limits of the analytical range for the associated test (as provided by UKB).

```{r biomarker-distributions, fig.asp=0.5}
for (bm in biomarkers) {
  raw_bm <- biomarkers_raw[match(bm, biomarkers)]
  raw_hist <- ggplot(raw_phenos, aes_string(x = raw_bm)) +
    geom_histogram(bins = 30) +
    geom_vline(xintercept = analytical_ranges[[raw_bm]][1], linetype = "dashed") +
    geom_vline(xintercept = analytical_ranges[[raw_bm]][2], linetype = "dashed") +
    labs(x = biomarkers_short[match(bm, biomarkers)],
         y = "Sample size",
         title = paste0(biomarkers_clean[match(bm, biomarkers)], " (raw)"))
  n_nonmissing <- sum(!is.na(phenos[[bm]]))
  preprocessed_hist <- ggplot(phenos, aes_string(x = bm)) +
    geom_histogram(bins = 30) +
    labs(x = biomarkers_short[match(bm, biomarkers)],
         y = "Sample size",
         title = paste0(biomarkers_clean[match(bm, biomarkers)], " (preprocessed)"),
         subtitle = paste0(bm, " (N = ", n_nonmissing, ")"))
  print(plot_grid(raw_hist, preprocessed_hist, nrow = 1, align = "h"))
}
```

## Diet preprocessing

Dietary data came from multiple sources:

* Food frequency questionnaires, given to all participants during their assessment center visit(s).
* Online 24-hour dietary questionnaires, collected at anywhere from one to five timepoints including the assessment center visit (for the final ~70k participants) and online between approximately Feb 2011 - Apr 2012.

The following QC and preprocessing steps were performed for data from the 24-hour dietary questionnaires:

1. Exclude questionnaires having reported daily caloric intake <600 or >4800 kcals/day
2. Exclude questionnaires for which the participant reported that dietary intake that day was not typical (UKB field 100020)
3. Take the mean for each basic dietary variable (single foods/nutrients) over all questionnaires returned by a given participant
4. Calculate derived values (for example, the MUFA:SFA ratio)
5. Winsorize all diet quantities (including derived values) at 3 SDs from the mean
6. Calculate a 9-item Mediterranean diet score (MDS) based on the method described by Carter et al. 2019 *J. Nutr. Sci.*. This score assigns one point for intakes below (unhealthy) or above (healthy) the median population value (other than alcohol, which is assigned based on specific intake thresholds).

```{r diet-variables}
dr_nutrient_fields <- c(
  TCALS = "26002",
  CHO = "26013", SUCROSE = "26059", 
  FAT = "26008", SFA = "26014", MUFA = "26032", PUFA = "Calculated",
  N3FA = "26015", N6FA = "26016",
  PRO = "26005", ALC = "26030", FIBER = "26017", 
  NUT_FE = "26019", NUT_NA = "26025", NUT_K = "26024", NUT_FOL = "26022",
  NUT_MG = "26025", NUT_VITC = "26023", NUT_VITD = "26029"
)
dr_nutrient_fields_clean <- c(
  "Total calories",
  "Carbohydrates", "Sucrose", 
  "Dietary fat", "Saturated fat", "Monounsaturated fat", "Polyunsaturated fat", 
  "Omega-3 fatty acids", "Omega-6 fatty acids",
  "Protein", "Alcohol", "Fiber", 
  "Iron", "Sodium", "Potassium", "Folate", "Magnesium", "Vitamin C", "Vitamin D"
)
dr_food_group_fields <- setNames(
  rep("Aggregate", 7),
  c("VEG", "LEGUMES", "FRUIT", "NUTS", "FISH", "WHGRAIN", "REDPRMEAT")
)
dr_food_group_fields_clean <- c(
  "Vegetables", "Legumes", "Fruit", "Nuts", "Fish", "Whole grains", 
  "Red and processed meat"
)

# ffq_fields <- c(
#   oily_fish = 1329, nonoily_fish = 1339, prmeat = 1349, poultry = 1359, 
#   beef = 1369, lamb = 1379
# )
ffq_fields <- c(
  cooked_veg = 1289, raw_veg = 1299,
  fresh_fruit = 1309, dried_fruit = 1319,
  oily_fish = 1329, nonoily_fish = 1339,
  prmeat = 1349, poultry = 1359,
  beef = 1369, lamb = 1379,
  whole_bread = 1448
)
ffq_fields_clean <- c(
  "Cooked vegetables", "Raw vegetables", "Fresh fruit", "Dried fruit",
  "Oily fish", "Non-oily fish", "Processed meat", "Poultry", "Beef", "Lamb",
  "Wholemeal/whole grain bread vs. other"
)

supp_fields <- c(fish_oil_24hr = "20084", fish_oil_touchscreen = "6179",
                 fish_oil_verbal = "20003")
supp_fields_clean <- c("Fish oil (24HR)", "Fish oil (touchscreen)", 
                       "Fish oil (verbal interview)")

all_diet_fields <- names(c(
  dr_nutrient_fields, dr_food_group_fields, ffq_fields, supp_fields
))
all_diet_field_ids <- c(
  dr_nutrient_fields, dr_food_group_fields, ffq_fields, supp_fields
)
all_diet_fields_clean <- c(
  dr_nutrient_fields_clean, dr_food_group_fields_clean, ffq_fields_clean, 
  supp_fields_clean
)

tibble(
  `Dietary trait` = all_diet_fields_clean,
  Abbreviation = all_diet_fields,
  `UKB field` = all_diet_field_ids,
  Source = rep(c("24-hour dietary questionnaire", "Food frequency questionnaire", 
                 "Supplement questionnaire"),
               c(length(dr_nutrient_fields) + length(dr_food_group_fields), 
                 length(ffq_fields), length(supp_fields)))
) %>%
  kable(caption = "Relevant dietary fields") %>%
  kable_styling(full_width=FALSE)

mds_components <- c("VEG", "LEGUMES", "FRUIT", "NUTS", "FISH", "WHGRAIN", 
                   "MUFA2SFA", "REDPRMEAT", "ALC")
mds_components_clean <- c("Vegetables", "Legumes", "Fruit", "Nuts", "Fish",
                         "Whole grains", "MUFA-to-SFA ratio", 
                         "Red and processed meat", "Alcohol")
md_component_cats <- c(rep("Healthy", 7), "Unhealthy", "Mixed")
md_component_thresholds <- c(rep("Greater than median", 7), "Less than median",
                            ">5 and <25 g/day")
tibble(
  `MDS component` = mds_components_clean,
  Abbreviation = mds_components,
  Category = md_component_cats,
  Threshold = md_component_thresholds
) %>%
  kable(caption = "Mediterranean diet score components and calculation") %>%
  kable_styling(full_width=FALSE)
```

```{r num-recalls}
table(phenos$num_recalls) %>%
  as.data.frame() %>%
  setNames(c("# recalls completed", "N")) %>%
  kable(caption = "Sample sizes available with 24HR data") %>%
  kable_styling(full_width = F)
```

These distributions contain all available values, including repeat measurements per individual where available.

```{r diet-distributions, out.width="70%"}
for (dv in c("mds", all_diet_fields)) {
  clean_dv <- if (dv == "mds") {
    "Mediterranean diet score"
    } else {
      all_diet_fields_clean[match(dv, all_diet_fields)]
    }
  n_nonmissing <- sum(!is.na(phenos[[dv]]))
  dv_hist <- ggplot(phenos, aes_string(x=dv)) +
    geom_histogram(bins=30) +
    labs(x=dv,
         y="Sample size",
         title=paste0(clean_dv, " (N = ", n_nonmissing, ")"))
  print(dv_hist)
}
```
